Approximation as Differentiation notes

### 2025-02-26 notes/sec/grothendieck.tex
Restructure a bit.
Give type of (−,𝑖) for clarify.
Onto g'.

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),W)$ in $\Fam(C)$ where $W$ is the indexed family which maps
every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $\Fam(C)(X,Y)$ to $\prod_{i \in I}\reindex{Y}{f}_i$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ where:
\begin{itemize}
\item $f'(i) = (f \comp (i, -): J \to K, \{g_{i,j} \comp \inj_{Y_j}\}_{j \in J}: \Fam(J,C))$
\item $g'(i) = $.
\end{itemize}
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}

>>>>

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where (overloading notation) $[X,Y]$ is
the indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $\Fam(C)(X,Y)$ to $\prod_{i \in
I}\reindex{Y}{f}_i$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ where:
\begin{itemize}
\item $f'(i) = (f \comp (i, -): J \to K, \{g_{i,j} \comp \inj_{Y_j}\}_{j \in J}: Y \to \reindex{Z}{f \comp (i,
-)})$
\item $g' = \{\}_{i \in I}$.
\item $(-, i)$ is the reindexing function $j \mapsto (i, j): J \to I \times J$
\end{itemize}
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}
